Stateless Model Checking with Data-Race Preemption Points

### 2015-10-16 pldi-16/related.tex
rephrase

\newcommand\portend{\textsc{Portend}}
\portend~\cite{portend} is the most closely related work we have found.
It performs a single-pass analysis as normal, then explores a limited state space to classify candidates in a taxonomy of likely severity.
Compared to us, \portend~can detect non-failing races which nevertheless cause suspiciously different program output,
while we depend on directly detecting failures.
It also uses symbolic execution to test input nondeterminism along with schedule nondeterminism,
while we explore the latter only.
However, \portend~does not perform MC-like exploration in advance of knowing data-race locations,
which we showed in \sect{\ref{sec:eval-falseneg}} can miss some bugs.
It is also limited to the POSIX synchronization API, so cannot verify lock implementations such as we do with \mxtest.
Future work could combine the two approaches, using \landslide~to produce new traces for \portend~to classify, or using \portend's analysis to inform \quicksand's state space priorities.

>>>>

\newcommand\portend{\textsc{Portend}}
\portend~\cite{portend} is the most closely related work we have found.
It performs a single-pass analysis as normal, then explores a limited state space to classify candidates in a taxonomy of likely severity.
Compared to us, \portend~can detect non-failing races which nevertheless cause suspiciously different program output,
while we depend on directly detecting failures.
It also uses symbolic execution to test input nondeterminism along with schedule nondeterminism,
while we explore the latter only.
However, \portend~does not explore alternate interleavings in advance of knowing data-race locations,
which is necessary to expose some bugs (\sect{\ref{sec:eval-falseneg}}).
It is also limited to the POSIX synchronization API, so cannot verify lock implementations such as we do with \mxtest.
Future work could combine the two approaches, using \landslide~to produce new traces for \portend~to classify, or using \portend's analysis to inform \quicksand's state space priorities.
